---
title: Introduction to Data Science Final Project 
subtitle: Project Wine
output: html_document
author: Jonas, Eddie, Rishav, Anant
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project Proposal  

### Data Information
**Data: (5 points) Describe the data set you have chosen and where it comes from. If it has a license (such as a Creative Commons license), mention it. If it does not have a license, explain why you believe you are allowed to use these data for this project.**

The data set we have chosen are related to red and white variants of the Portuguese "Vinho Verde" wine. There are a total of 12 inputs variables obtained using physicochemical tests in the data set, which are: 
1 - fixed acidity  
2 - volatile acidity  
3 - citric acid  
4 - residual sugar  
5 - chlorides  
6 - free sulfur dioxide  
7 - total sulfur dioxide  
8 - density  
9 - pH  
10 - sulphates  
11 - alcohol  
Output variable (based on sensory data):  
12 - quality (score between 0 and 10)  

The dataset is from https://archive.ics.uci.edu/ml/datasets/wine+quality and is donated to the UCI Machine Learning Repository. It is available for use on this project by including the following citation:  

P. Cortez, A. Cerdeira, F. Almeida, T. Matos and J. Reis.
Modeling wine preferences by data mining from physicochemical properties. In Decision Support Systems, Elsevier, 47(4):547-553, 2009.

### Research Questions 

**Research questions: (6 points) Come up with at least three research questions that you want to answer using these data. Make sure that at least two of these questions involve at least three variables. You are welcomed to create new variables based on existing ones. Note that you will have the option to update / revise / change these questions for your presentation at the end of the semester.**

**Research Question 1:**  
Just knowing the concentration of the chemical compounds, are we able to predict whether they are red wine or white wines?

We will use logistic regression or decision trees to do so.

**Research Question 2:**  
Predict quality of wine using regression (lasso) for red and white separately, as well as together

- can split into bands (bad, good) or more 
- add label column 

**Research Question 3:**  
Clustering after finding the significant variables using stepwise regression.

-- scatterplot matrix? 


### EDA

**EDA: (9 points) Perform exploratory data analysis (EDA) that addresses, but not necessarily fully answers, each of the three research questions you outlined above. Your EDA should contain numerical summaries and visualizations. Each R output or plot should be accompanied by a brief interpretation. Do not use more than 2 plots per research question.**


```{r}
## Data and necessary libraries

redwine_data <- read.csv("winequality-red.csv")
whitewine_data <- read.csv2("winequality-white.csv")

whitewine_data[] <- lapply(whitewine_data, function(x) {
    if(is.factor(x)) {
      as.numeric(as.character(x))
      }
  else x
})
sapply(whitewine_data, class)

redwine_data$type <- "red"
whitewine_data$type <- "white"

wine_data <- rbind(redwine_data, whitewine_data)
```

```{r}

summary(redwine_data)
summary(whitewine_data)
summary(wine_data)

```

```{r}
pairs(redwine_data[,c(1:12)])
```

```{r}
pairs(whitewine_data[,c(1:12)])
```

```{r}
pairs(wine_data[,c(1:12)])

```


```{r}

boxplot(redwine_data$quality)
hist(redwine_data$quality)

```

### Timeline  
**Timeline: (2 points) Sketch out a timeline for the work you will do each week to complete this project. Be realistic – discuss course schedules, travel plans, etc.**

Our project would proceed in the following 3 stages:

Stage 1: Proposal and Methodology

Week 10: 19 - 25 October

We will be working on the proposal, mainly on the EDA and thinking about the research questions for Wednesday's submission, and we will continue refining the research questions and the methodology to answer each research question for the rest of the week. Ideally, we would try and combine the research questions together to form a more nuanced research question that combines a few techniques.

We assume that the feedback for the proposal will be back by Friday 23 October.

Week 11: 26 October - 1 November

For the start of Week 11, we will continue refining the research questions and decide on the methodology based on the feedback for the proposal. By Tuesday (27 October), we should have this finalized.

Stage 2: Data Analysis

Week 11: 26 October - 1 November

For the second half of Week 11, we will begin doing the data analysis for the research questions according to the methodology that we had set previously. By Friday (30 October), we will present initial results to each other for each of our subparts and decide on the next course of action.

Week 12: 2 - 8 November

We will continue doing data analysis based on the comments that we give each other during the initial results check-in the previous week. We would have another check-in on Tuesday or Wednesday (3-4 November) to present new findings. We will give comments to each other, but at this stage the analysis should be nearing completion. 

If we do have any changes to make based on comments on Wednesday, we finalize the results by Friday. On Friday, we will have a small discussion on how best to visualize our results and who should take charge of which subsection of our project, which leads into our next stage.

Stage 3: Presentation 

Week 13: 9 - 13 November

Based on the discussion we had on the presentation, we will work on our individual subparts until Tuesday on a shared slides document, updating each other along the way. On Tuesday and Wednesday, we will meet up to practice the presentation and to cohere our individual subparts together. Over the next few days, we will continuing doing so until we present on 13 November.

Deadline: 13 Nov

### Teamwork  
**Teamwork: (3 points) Describe in detail how you will divide up the work between team members and what aspects of the project you will complete together as a team. Note that during the presentation session each member needs to be able to answer questions about all aspects of the work, regardless of whether they took the lead on that section or not.**

Again, we discuss this section in terms of the 3 stages we outlined in our timeline.

Stage 1: Proposal and Methodology

We will be doing the data set-up and cleaning, as well as the EDA for the proposal together. Following the submission of the proposal, we will be continuing to work as a team to refine the research questions and confirm on the methodology for the research question together as a team. 

Ideally, we would have at least three subsections for the three research questions that we submit for our proposal. For the rest of this section, we assume we have three subsections, one for each research question.

Stage 2: Data Analysis

Assuming three subsections, we will be splitting it up into two smaller teams:

- Subsection 1: two people
- Subsection 2: one people
- Subsection 2: one people

We would be deciding this based on interest and which would take the most effort once we finalize the methodology. That means that each subsection has at least one person taking charge. Even so, we would have regular check-ins (Tuesdays/ Wednesdays and Fridays) to keep each other updated and to give each other comments. This ensures that each team member knows what is going on for the entire project.

Stage 3: Presentation 

The initial stages for the preparation for the presentation would be done by the subsections decided above. These initial stages refer to expressing the results in terms of nice visuals.

Once we meet on Tuesday or Wednesday, we would be working together to combine the presentation into a coherent narrative.





