---
title: "Wine Quality Data Project"
author: "Anant Jain, Eddie Lim, Joanas Tan, Rishav Koirala"
date: "11/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(e1071)
library(caret)
library(ROCR)

```

### Introduction 

**Data Information**  
The data set we have chosen are related to red and white variants of the Portuguese "Vinho Verde" wine. There are a total of 12 inputs variables obtained using physicochemical tests in the data set, which are: 
1 - fixed acidity  
2 - volatile acidity  
3 - citric acid  
4 - residual sugar  
5 - chlorides  
6 - free sulfur dioxide  
7 - total sulfur dioxide  
8 - density  
9 - pH  
10 - sulphates  
11 - alcohol  
Output variable (based on sensory data):  
12 - quality (score between 0 and 10)  

**Research Question**  
Can we predict with good accuracy the quality of wine for both the red and the white varieties by considering their chemical properties, and identify the most significant predictors that make a good red wine or white wine? 

**Research Approach**  
01 - EDA  
* Representing each variable as a boxplot  
* Scatterplot matrix  

02 - Building Predictors  
* Logistic Regression  
* Decision Tree  
* Naive Bayes  

03 - Identifying Significant Predictors  
* PCA  
* Stepwise Regression  

### Preparing the data 

```{r}
data_allwine <- read.csv("~/projects/yalenus/IntroToDSProject/wine.csv")
data_redwine <- read.csv("~/Desktop/YaleNUS/Y3S1/IntrotoDS/Assignments/DSProj_NaiveBayes/winequality-red.csv")
data_whitewine <- read.csv("~/Desktop/YaleNUS/Y3S1/IntrotoDS/Assignments/DSProj_NaiveBayes/winequality-white.csv", sep=";")
```

### Exploratory Data Analysis (EDA)

**Boxplots of each variable by type of wine (red/white)**  

```{r}

# box-and-whiskers plot for each variable by type
par(mfrow=c(2,3))

for(i in 1:11){
  boxplot(data_allwine[,i] ~data_allwine$type, ylab = names(data_allwine)[i])
}
```

**Exploring Correlation Between Variables** 

TO ADD: exploration on correlation between variables + explanation on approach of dropping of variables (textbook)


Since the classifiers we are evaluating (Logistic Regression, Naive Bayes and Decision Trees) do not handle correlated features well, we can directly work with only the variables we have chose to keep in our dataset:

```{r}
# Retained variables for red 
# citric.acid + residual.sugar + chlorides + free.sulfur.dioxide + sulphates + alcohol

vars_red <- c("citric.acid", "residual.sugar", "chlorides", "free.sulfur.dioxide", "sulphates", "alcohol", "quality")
data_redwine<- data_redwine[vars_red]

# Retained variables for white
# fixed.acidity + volatile.acidity + citric.acid + residual.sugar + chlorides + free.sulfur.dioxide + sulphates

vars_white <- c("fixed.acidity", "volatile.acidity", "citric.acid", "residual.sugar", "chlorides", "free.sulfur.dioxide", "sulphates", "quality")
data_whitewine <- data_whitewine[vars_white]


```


### Building Predictors 

**Assign Labels**  
```{r}

data_all_wine_labelled <- mutate(data_allwine,
                                 label = case_when(
                                   quality > 6 ~ "good", 
                                   quality <= 6 ~ "bad"
                                 ))

data_red_wine_labelled <- mutate(data_redwine,
       label = case_when(
         quality > 6 ~ "good", 
         quality <= 6 ~ "bad"
       ))

data_white_wine_labelled <- mutate(data_whitewine,
                                label = case_when(
                                  quality > 6 ~ "good", 
                                  quality <= 6 ~ "bad"
                                ))

```

**Naive Bayes**  

**All Wines**  
```{r}
### All Wine NB Analysis
# Note that 'type' is also used as a feature in predicting quality here

indxTrain_allwine <- createDataPartition(y = data_all_wine_labelled$label ,p = 0.8,list = FALSE) # uses random sampling
traindata_allwine <- data_all_wine_labelled[indxTrain_allwine, !(names(data_all_wine_labelled) %in% c('quality'))]
testdata_allwine <- data_all_wine_labelled[-indxTrain_allwine, !(names(data_all_wine_labelled) %in% c('quality'))]

nb_model_allwine <- naiveBayes(as.factor(label) ~ . , traindata_allwine, laplace=.01)

nb_prediction_allwine <- predict(nb_model_allwine,
                         # remove column "label"
                         testdata_allwine[,!(names(data_all_wine_labelled) %in% c('label'))],
                         type='raw') 

score_allwine <- nb_prediction_allwine[, c("good")]

actual_class_allwine <- testdata_allwine$label == 'good' 
pred_allwine <- prediction(score_allwine, actual_class_allwine)
perf_allwine <- performance(pred_allwine, "tpr", "fpr")
```

```{r}
plot(perf_allwine, lwd=2, xlab="False Positive Rate (FPR)", ylab="True Positive Rate (TPR)")
abline(a=0, b=1, col="gray50", lty=3)
```


```{r}
auc_allwine <- performance(pred_allwine, "auc")
auc_allwine <- unlist(slot(auc_allwine, "y.values"))
auc_allwine
```


**White Wine**
``` {r}
### White Wine NB Analysis
indxTrain_white <- createDataPartition(y = data_white_wine_labelled$label ,p = 0.8,list = FALSE)
traindata_white <- data_white_wine_labelled[indxTrain_white, !(names(data_white_wine_labelled) %in% c('quality'))]
testdata_white <- data_white_wine_labelled[-indxTrain_white, !(names(data_white_wine_labelled) %in% c('quality'))]

nb_model_white <- naiveBayes(as.factor(label) ~ . , traindata_white, laplace=.01)

nb_prediction_white <- predict(nb_model_white,
                         # remove column "label"
                         testdata_white[,!(names(data_white_wine_labelled) %in% c('label'))],
                         type='raw') 

nb_score_white <- nb_prediction_white[, c("good")]

actual_class_white <- testdata_white$label == 'good' 
nb_pred_white <- prediction(nb_score_white, actual_class_white)
nb_perf_white <- performance(nb_pred_white, "tpr", "fpr")

```


``` {r}
plot(nb_perf_white, col="blue", lwd=2, xlab="False Positive Rate (FPR)", ylab="True Positive Rate (TPR)")
abline(a=0, b=1, col="gray50", lty=3)
```


``` {r}
nb_auc_white <- performance(nb_pred_white, "auc")
nb_auc_white <- unlist(slot(nb_auc_white, "y.values"))
nb_auc_white

```

**Red Wine**
``` {r}

indxTrain <- createDataPartition(y = data_red_wine_labelled$label ,p = 0.8,list = FALSE) # uses random sampling
traindata <- data_red_wine_labelled[indxTrain, !(names(data_red_wine_labelled) %in% c('quality'))]
testdata <- data_red_wine_labelled[-indxTrain, !(names(data_red_wine_labelled) %in% c('quality'))]

nb_model_red <- naiveBayes(as.factor(label) ~ . , traindata, laplace=.01)

nb_prediction_red <- predict(nb_model_red,
                         # remove column "label"
                         testdata[,!(names(data_red_wine_labelled) %in% c('label'))],
                         type='raw') 

nb_score_red <- nb_prediction_red[, c("good")]

actual_class_red <- testdata$label == 'good' 
nb_pred_red <- prediction(nb_score_red, actual_class_red)
nb_perf_red <- performance(nb_pred_red, "tpr", "fpr")

```

``` {r}
plot(nb_perf_red, lwd=2, xlab="False Positive Rate (FPR)", ylab="True Positive Rate (TPR)")
abline(a=0, b=1, col="gray50", lty=3)
```

``` {r}
nb_auc_red <- performance(nb_pred_red, "auc")
nb_auc_red <- unlist(slot(nb_auc_red, "y.values"))
nb_auc_red
```


**Side-by-side Plot**

``` {r}
par(mfrow=c(1,2)) 
plot(nb_perf_red, col="red", lwd=2, main="Red Wine Quality Label NB Model Prediction Perf", xlab="False Positive Rate (FPR)", ylab="True Positive Rate (TPR)")
abline(a=0, b=1, col="gray50", lty=3)
plot(nb_perf_white, col="blue", lwd=2, main="White Wine Quality Label NB Model Prediction Perf", xlab="False Positive Rate (FPR)", ylab="True Positive Rate (TPR)")
abline(a=0, b=1, col="gray50", lty=3)
```

**Multiple lines in single plot**
``` {r}
par(mfrow=c(1,1)) 
plot(nb_perf_red, col="red", lwd=2, main="All Wine Quality Label NB Model Prediction Perf", xlab="False Positive Rate (FPR)", ylab="True Positive Rate (TPR)")
abline(a=0, b=1, col="gray50", lty=3)

# par(new = TRUE)  # We draw on top of the existing plot.
# plot(perf, col = "red", lwd=2, main="", xlab="", ylab="")

par(new = TRUE)  # We draw on top of the existing plot.
plot(nb_perf_white, col = "blue", lwd=2, main="", xlab="", ylab="")

legend("topleft",
       legend = c("Red Wine", "White Wine"),
       col = c("red", "blue"),
       pch = c(0, 0, 0))
```

**AUCs**
```{r}
print(paste0("AUC of NB Model (Red Wine):", nb_auc_red))
print(paste0("AUC of NB Model (White Wine):", nb_auc_white))
```